---
title: 'Coding 2: Final Term Project'
author: "Ali Sial"
date: "12/21/2021"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---


```{r setup, include=FALSE}
#rm(list=ls())

getwd()
library(tidyverse)
library(rvest)
library(xml2)
library(data.table)
library(esquisse)
library(dplyr)
library(ggplot2)
library(stringr)
library(tidyr)
library(hrbrthemes)
library(prettydoc)
library(ggthemes)
library(haven)
library(data.table)
library(rms)
library(pscl)
library(mfx)
library(kableExtra)
library(lspline)
library(reshape2)
library(dplR)
library(fixest)
library(dplyr)
library(AER)
library(ggpubr)
getwd()
```


## Aim of the assignment
The main goal of this project was to scrape all the data on aircraft and their manufacturers (including all specifications) from [AeroCorner.com]('https://aerocorner.com/manufacturers/'). There are a total of 110 manufacturers and 914 aircraft in total. The final data extracted contains 914 observations (aircraft names) and all it's specification that was available on the website, this is stored as 34 different variables. 

## Process Overviw
The data was store in three different links and 918 pages on the website, to extract the data, I created five functions. This data was stored in five different tables which were then combined to get on data table. Since running the functions used to retrieve data takes a lot of time when knitting the file, I decided to save the data in a CSV file and uploaded to my [GitHub]('https://github.com/alisial94/Web_Scrapping_Final_Project/blob/main/aircraft_data') repository. I will be calling the data used for analysis in this exercise using this. The code for the entire scrapping process is add to the Rmd file as text and can also be retrieved from the same [GitHub]('https://github.com/alisial94/Web_Scrapping_Final_Project/blob/main/Code') repository.

## Data Cleaning & Munging
The final scrapped dataset was very unorganised, thus required some cleaning before it could be used for analysis. All the table's type was character and rather than munging all the data, I decided to filter the tables that were needed for my analysis and adjusted them to our requirements. 

## Analysis
The second goal of this project was to produce some meaning full questions that this data can answer and provide us with some insides about the Avionics Industry. The three questions that I would be visualising with this data are:

- Count of different aircraft each manufacturer produces. 
- To understand if there is a liner relation between Price of the Aircraft and it's Horse Power
- To uncover pattern of association between the Fuel Economy of aircrafts and their Fuel Tank Capacity



```{r, include= FALSE}
# first part getting the link for the main page
#p <- read_html("https://aerocorner.com/manufacturers/")
#name <- p %>% html_nodes('.list-manufacturers .py-1 .py-1') %>% html_text()
#link <- p %>% html_nodes('.list-manufacturers .py-1 .py-1') %>% html_attr('href') 
#df <- data.frame('Name' = name, 'link' = link)

# getting the 
#get_company <- function(url) {
#  l <- read_html(url)
#  list_x <- list()
#  #entity <- l %>% html_nodes('.entry-title') %>% html_text()
#  list_x[['link2']] <- l %>% html_nodes('.py-1 a') %>% html_attr('href')
#  list_x[['name2']] <- l %>%  html_nodes('.py-1 a') %>% html_text()
#  #list_x[['company']] <- replicate(length(name2), entity)
#  return(list_x)
#}

#url <- df$link
#dfx <- lapply(url, get_company)
#dfx1 <- rbindlist(dfx, fill = T)

# First Table
#get_info <- function(url2) {
#  x <- read_html(url2)
#  list_y <- list()
#  list_y[['name']] <- x %>%  html_nodes('.entry-title') %>% html_text()
#  list_y[['manufacturer']] <- x %>%  html_nodes('#main .mb-0:nth-child(2)') %>% html_text()
#  list_y[['country']] <- x %>%  html_nodes('#main .mb-0:nth-child(4)') %>% html_text()
#  list_y[['manufactured']] <- x %>%  html_nodes('.mb-0:nth-child(6)') %>% html_text()
#  list_y[['ICAO']] <- x %>%  html_nodes('.mb-0:nth-child(8)') %>% html_text()
#  list_y[['price']] <- x %>%  html_nodes('.mb-0:nth-child(10)') %>% html_text()
#return(list_y)
#}


#url2 <- dfx1$link2
#list_aircraft <- lapply(url2, get_info)
#df_aircraft <- rbindlist(list_aircraft, fill = T)

#df_aircraft<- df_aircraft[-c(7, 20, 64, 75, 81, 83, 98, 122, 124, 208, 237, 239,
#                             241, 243, 274, 276, 288, 345, 357, 398, 400, 402,
#                             429, 470, 500, 502, 504, 506, 528, 531, 533, 535, 537,
#                             580, 582, 589, 591, 595, 602, 619, 701, 703, 705, 707,
#                             710, 723, 725, 727, 729, 732, 740, 783, 788, 790, 808, 
#                             846, 865, 878, 880, 883, 887, 891, 893, 895, 919, 933), ]


#Second Table
#get_details <- function(url2) {
#  x <- read_html(url2)
#  list_z <- list()
#  list_z[['name']] <- x %>%  html_nodes('.entry-title') %>% html_text()
#  keys2 <- x %>% html_nodes('.col-sm-5') %>% html_text()
#  values2 <- x %>% html_nodes('.col-sm-7') %>% html_text()
#  for( i in 1:length(keys2)) {
#    list_z[[ keys2[i] ]] <- values2[i]
#  }
#return(list_z)
#}

#url2 <- dfx1$link2
#get_details_list <- lapply(url2, get_details)
#df_spec1 <- rbindlist(get_details_list, fill = T)



#Third Table

#get_details_1 <- function(url2) {
#  x <- read_html(url2)
#  list_a <- list()
#  list_a[['name']] <- x %>%  html_nodes('.entry-title') %>% html_text()
#  keys3 <- x %>% html_nodes('#weights .col-lg-5') %>% html_text()
#  values3 <- x %>% html_nodes('#weights .col-lg-7') %>% html_text()
#  for( i in 1:length(keys3)) {
#    list_a[[ keys3[i] ]] <- values3[i]
#  }
#  return(list_a)
#}

#get_details_list_1 <- lapply(url2, get_details_1)
#df_spec2 <- rbindlist(get_details_list_1, fill = T)





#Fourth Table

#get_details_2 <- function(url2) {
#  x <- read_html(url2)
#  list_b <- list()
#  list_b[['name']] <- x %>%  html_nodes('.entry-title') %>% html_text()
#  keys4 <- x %>% html_nodes('#dimensions .col-lg-5') %>% html_text()
#  values4 <- x %>% html_nodes('#dimensions .col-lg-7') %>% html_text()
#  for( i in 1:length(keys4)) {
#    list_b[[ keys4[i] ]] <- values4[i]
#  }
#  return(list_b)
#}

#get_details_list_2 <- lapply(url2, get_details_2)
#df_spec3 <- rbindlist(get_details_list_2, fill = T)



#final_aircraft_data <- cbind(dfx1,df_aircraft,df_spec1,df_spec2,df_spec3)

#final_aircraft_data<- final_aircraft_data[, -c(2,9,21,27)]

#final_aircraft_data$links <- final_aircraft_data$link2

#final_aircraft_data<- final_aircraft_data[, -c(1)]

#View(final_aircraft_data)

# saving the entire data scrapped into a CSV so it is easier to run the Rmd file
#write_csv( final_aircraft_data , 'aircraft_data' )

```



```{r,include=FALSE}
# calling data from git 

aircraft_data <- read_csv(url("https://raw.githubusercontent.com/alisial94/Web_Scrapping_Final_Project/main/aircraft_data")) 

## Cleaning and Mungging data

## Filtering data
viz_data <- aircraft_data %>%
  filter(!(`Seats - First Class:` %in% "\n ")) %>%
  filter(!(`Wing Tips:` %in% 
             "\n ")) %>%
  filter(!is.na(name))
   
#removing the unwanted columns
viz_data <- viz_data[, c(1,2,3,6,9,13,21)] 
view(viz_data)
# extracting the price in millions from the string variable
viz_data$Price <- as.numeric(gsub(".*?([0.0000001-9.99]+).*", "\\1", viz_data$price)) 

#converting the power in pound force to horsepower in new column
viz_data$pound_force <- ifelse(grepl('pound-force', viz_data$`Power:`),viz_data$`Power:`,"")
viz_data$pound_force <- gsub('pound-force', '', viz_data$pound_force)
viz_data$pound_force <- as.numeric(gsub(",","",viz_data$pound_force))
viz_data$pound_force <- (viz_data$pound_force/500)*60

#fixing the power that is in horsepower in a new column
viz_data$horse_power <- ifelse(grepl('horsepower', viz_data$`Power:`),viz_data$`Power:`,"")
viz_data$horse_power <- gsub('horsepower', '', viz_data$horse_power)
viz_data$horse_power <- as.numeric(gsub(",","",viz_data$horse_power))


#combining the two new created tables
viz_data$Horsepower <- paste0(viz_data$horse_power, viz_data$pound_force)

#removing the NA in the values and saving it as numeric
viz_data$Horsepower <- gsub('NA', '', viz_data$Horsepower)
viz_data$Horsepower <- as.numeric(viz_data$Horsepower)

#fixing the column Fuel Economy
viz_data <- separate(data = viz_data,
                     col = "Fuel Economy:",
                     into = c("nm/g", "km/l"),
                       sep = "/")


viz_data$`nm/g` <- gsub('nautical mile', '', viz_data$`nm/g`)
viz_data$Fuel_Eco <- as.numeric(gsub(",","",viz_data$`nm/g`))


#fixing the column Fuel Tank Capacity
viz_data$fuel_tank_Cap<-gsub("g.*","",viz_data$`Fuel Tank Capacity:`)
viz_data$fuel_tank_Cap <- as.numeric(gsub(",","",viz_data$fuel_tank_Cap))
```

```{r, include=FALSE}
# Total number of different aircraft each manufacturer produces
Viz1 <-viz_data %>%
  ggplot() +
  aes(x = manufacturer) +
  geom_bar(fill = "seagreen3") +
  labs(x = "Manufacturer", 
       y = "Count of Aircraft ", title = "Aircrafts per Manufacturer") +
  ggthemes::theme_economist_white()+
  theme( axis.text.x = element_text(angle = 60, vjust = 1,
                                    size = 6, hjust = 1))

Viz1



# Linear Regression Price Vs Power
Viz2 <-  viz_data %>% 
  filter(Horsepower <= 10000) %>%
  filter(Price <= 500) %>% 
  ggplot( aes(x = log(Horsepower), y = log(Price))) +
  geom_point(color='seagreen3',size=2,alpha=0.6) +
  geom_smooth(method="lm" , formula = y ~ x )+
  labs(x = "Log Horse Power", y = "Log Price (US$ in Million)") +
  ggthemes::theme_economist_white()


Viz2

regPvP <- feols( log(Price) ~ log(Horsepower), data=viz_data, vcov = 'hetero' )
summary( regPvP )


# Linear Regression Fuel Economy Vs Fuel Tank Size
Viz3 <- viz_data %>% 
  filter(fuel_tank_Cap <= 60000) %>%
  filter(Fuel_Eco <= 30) %>% 
  ggplot( aes(x = log(fuel_tank_Cap), y = log(Fuel_Eco))) +
  geom_point(color='seagreen3',size=2,alpha=0.6) +
  geom_smooth(method="lm" , formula = y ~ x )+
  labs(x = "Log Fuel Tank Capacity (Gallon)", y = "Log Fuel Economy (nautical mile per gallon)") +
  ggthemes::theme_economist_white()

Viz3

regEvC <- feols( log(fuel_tank_Cap) ~ log(Fuel_Eco), data=viz_data, vcov = 'hetero' )
summary( regEvC  )
```


## Number of Aircrafts by Manufacturers
As stated above there are a total of 110 manufactures, the chart below shows the different number of aircraft they produce. Observing the chart we can tell that Cessna has the largest portfolio, while majority of the manufactures produce less than 10 kinds of aircraft. 

```{r, echo=FALSE, warning=FALSE, fig.width=10, fig.height = 5, fig.align="center"}
Viz1
```


## Linear Relation Between Price Vs Horse Power
Here, I wanted to check if the price of aircraft is somehow correlated with it's horse power. This means that when the horse power increase the price should either increase or  decrease. The graph below depicts that the linear relation between these the two variables, and it appears to be positive which means with and increase in horse power the price also increases. To further validate this observation, I ran a regression for these variables and the $\beta$ coefficient suggests that price to increase by 1.67% if horse power is higher by 1%.

```{r, echo=FALSE, warning=FALSE, fig.width=10, fig.height = 5, fig.align="center"}
Viz2
```


## Linear Relation between Fuel Economy Vs Fuel Tank Size
To examine this pattern of association, again I created a linear model and the graph below presents the results. As you can observe that this to has a linear relation but this time the trend is negative. This means that if the fuel tank capacity of aircraft increases the the fuel economy will decrease. The regression analysis also estimates a similar relation. The $\beta$ coefficient suggests that if the fuel capacity increase by 1% the fuel economy will decrease by 1.3%, thus a negative correlation. 

```{r, echo=FALSE, warning=FALSE, fig.width=10, fig.height = 5, fig.align="center"}
Viz3
```


## Conclusion
Overall, this project was a great learning experience about how data can easily be obtained form different sources when we don't have a read made data available for the analysis we intend to perform. The questions that I wanted to analyse in this project have also been answered well by the data. I understand the analysis performed is not very reliable be it provides the viewer with a starting point to further expand the horizon of this analysis. 




